Race results from the twelfth edition of the

### 2022-06-30 inst/volvo.Rmd
typo

Thus the first column refers to leg 1, in which competitor AbuDhavi
came first, Brunel third, and so on.  Here, `DNF` signifies "did not
finish" and `DNS` "did not start".  We can conver the table to a
support function with `ordertable2supp()`, remembering to specify the
noscore options:

>>>>

Thus the first column refers to leg 1, in which competitor Abu Dhabi
came first, Brunel third, and so on.  Here, `DNF` signifies "did not
finish" and `DNS` "did not start".  We can convert the table to a
support function with `ordertable2supp()`, remembering to specify the
noscore options:
